CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2023-12-21 paper.Rmd
Added link and reference to the CLPFUDatabase package

We created a suite of open-source `R` packages 
and the metapackage `CLPFUDatabase`
to assist SEA practitioners to analyze ECCs. 
The new packages enable analysis of any country in the world
across timespans of decades or longer.
In short, the new packages enable, for the first time, scalable SEA.
We used the new packages to create the CL-PFU database^["CL-PFU" 
is an initialism for "Country-Level
Primary, Final, and Useful."
The CL-PFU database contains many countries as well as 
continental and world aggregations.
Technically speaking, 
we create [matsindf][link-matsindf] data frames
stored as [pins][link-pins] on a pinboard, 
not SQL or similar databases.],
a new resource for the SEA community [@Marshall:2023aa; @Brockway:2024aa].

>>>>

We created a suite of open-source `R` packages 
and the metapackage [CLPFUDatabase][link-clpfudatabase] [@Heun-CLPFUDatabase:2023]
to assist SEA practitioners to analyze ECCs. 
The new packages enable analysis of any country in the world
across timespans of decades or longer.
In short, the new packages enable, for the first time, scalable SEA.
We used the new packages to create the CL-PFU database^["CL-PFU" 
is an initialism for 
"Country-Level Primary, Final, and Useful."
The CL-PFU database contains many countries as well as 
continental and world aggregations.
Technically speaking, 
we create [matsindf][link-matsindf] data frames
stored as [pins][link-pins] on a pinboard, 
not SQL or similar databases.],
a new resource for the SEA community [@Marshall:2023aa; @Brockway:2024aa].
